Lasso_RCI_Response

### 2024-06-30 Lasso_RCI_Response.Rmd
Made JT plots manually

## Read in the dataset. 
```{r}
Mothership <- read_sav("~/Desktop/Coding/data/PHPoutcome_clean.sav")

#DF_1<- read_sav("~/Desktop/Coding/data/PHPoutcome_clean.sav")
```

@@

####  Export as CSV
write.csv(Mothership,"~/Desktop/Coding/data/Mothership_paper")

@@

### Export as CSV
write.csv(Mothership,"~/Desktop/Coding/data/Mothership_Diag_treat.csv")

@@

#install.packages('naniar')
library(naniar)
vis_miss(Mothership_Missing)
```

@@

#2. JT classification for anxiety
JTRCI (data = RCI_df_anx2, 
                  pre = "pre", 
                  post = "post", 
                  ppid = "ID1", 
                  reliability = .74, 
                  indextype = "JT", 
                  #JTcrit = "auto",
                  plottitle = "JT Indices For Anxiety")

ANX_JT_smol<- JTRCIdf

@@

write_csv(table1_tab_anx,"~/Downloads/table1_tab_anx.csv")
```

@@

table1_tab_dep
write_csv(table1_tab_dep,"~/Downloads/table1_tab_dep.csv")

@@

ataset visualizatoin
```{r}
# #install.packages("ggdist")
# library("ggdist")
# 
# Mothership_lasso |> 
#   ggplot( aes(x=Depression_Responder, y=CUDOS_pre, fill=Depression_Responder)) +
#     geom_boxplot() +
#    #viridis::scale_fill_viridis(discrete = TRUE, alpha=0.6) +
#     geom_jitter(color="black", size=.6 , alpha=0.9) +
#     theme(
#       legend.position="none",
#       plot.title = element_text(size=11)
#     ) +
# #    ggtitle("Pre scores of depression severity") +
#     xlab("Depression Severity") +
#     ylim(0,80)
# 
# Mothership_lasso|>
# ggplot( mapping=aes(x=Trauma_C)) +
#   geom_bar()
# 
# Mothership_lasso|>
# ggplot( mapping=aes(x= Current_Dx)) +
#         geom_histogram() +
#     theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
#   theme(panel.background=NULL)+
#   theme(legend.title = element_blank()) 
#

@@

@@

#####  using 1se
# Final model with lambda.1se
lasso.model.1se.dep <- glmnet(x.dep, y.dep, alpha = 1, family = "binomial",
                      lambda = cv.lasso.dep$lambda.1se,standardized = TRUE)
# Make prediction on test data
x.test <- model.matrix(Depression_Responder ~., test.data)[,-1]
probabilities <- lasso.model.1se.dep %>% predict(newx = x.test,type ="response")
predicted.classes <- ifelse(probabilities > 0.5, "Responder", "Non-Responder")

# Model accuracy rate
observed.classes <- test.data$Depression_Responder
Mean.predict.1se.dep <- mean(predicted.classes == observed.classes)

@@

# Make predictions
probabilities <- full.model.dep %>% predict(test.data, type = "response")
predicted.classes <- ifelse(probabilities > 0.5, "Responder", "Non-Responder")
# Model accuracy
observed.classes <- test.data$Depression_Responder
Mean.predict.full.model.dep <- mean(predicted.classes == observed.classes)

@@

tmp_coeffs <- coef(lasso.model.1se.dep, s = "lambda.1se")
Dep_coefs <-tmp_coeffs@Dimnames[[1]][tmp_coeffs@i + 1]
Dep_reg_coefs <- Dep_coefs[2:length(Dep_coefs)]
Dep_reg_coefs
```

@@

write_csv(FP.min.dep, "~/Downloads/FP.min.dep")
```
1se -
```{r}
tmp_coeffs <- coef(lasso.model.1se.dep, s = "lambda.1se")
Dep_coefs <-tmp_coeffs@Dimnames[[1]][tmp_coeffs@i + 1]
Dep_reg_coefs <- Dep_coefs[2:length(Dep_coefs)]
Dep_reg_coefs

@@

write_csv(FP.1se.dep, "~/Downloads/FP.1se.dep")
```

@@

write_csv(FP.min.dep, "~/Downloads/FP.min.dep")

@@

write_csv(dep_df, "~/Downloads/dep_df")
```

@@

write_csv(FP.min.anx, "~/Downloads/FP.min.anx")

@@

write_csv(anx_df, "~/Downloads/anx_df")

@@

Anxiety Plot
```{r}
ANX_FP <- 
  anx_df |>
  ggplot(aes(y = reorder(Variable, -order))) +
  #take away background
  theme_classic() +
  #make the forrest plot
  geom_linerange(aes(xmin=OR_low, xmax=OR_high),size = 1, show.legend = FALSE,
                color = ifelse(anx_df$p.adjusted < 0.05, "red", "darkgrey")) +
  geom_point(aes(x=OR), shape= 16,
             size=4,show.legend = FALSE,
             color = ifelse(anx_df$p.adjusted < 0.05, "red", "darkgrey")) +
  geom_point(aes(x=OR), shape= 1,
             size=4,show.legend = FALSE, color = "white") +
    geom_point(aes(x=OR), shape= 1,
             size=4.1,show.legend = FALSE, color = "white")+
# geom_errorbar(aes(xmin=OR_low, xmax=OR_high),width =.6, show.legend = FALSE) +
  #change x axis name
  labs(
    x="Odds Ratio",
    # title = "    Odds of Meeting Physical Activity Guidelines",
    subtitle ="Odds of Anxiety Non-Response")+
  #adjust the dimentions. 
  coord_cartesian(ylim = c(1,  length(anx_df$Variable)))+
  #add a line at 1 for reference 
  geom_vline(xintercept = 1,linetype="dashed",alpha = .50) + 
  #add anotations to help suggests what each side means.
  annotate("text", x = .6, y = length(anx_df$Variable) -1 , label = "Less Likely", size= 4) +
  annotate("text", x = 1.4, y = length(anx_df$Variable) -1, label = "More Likely",size= 4) +
  #Git rid of the Y - Axis
    theme(axis.line.y = element_blank(),
        axis.ticks.y= element_blank(),
        axis.text.y= element_blank(),
        axis.title.y= element_blank())

ANX_text <- 
  dep_df |>
  ggplot(aes(y = reorder(Variable, -order))) +
  geom_text(aes(x = 0, label = Variable), hjust = 0,
        fontface = ifelse(dep_df$Variable == "Variable","bold","plain")) +
  geom_text(aes(x = 1.1, label = Beta),
        hjust = 0,
        fontface = ifelse(dep_df$Beta == "Beta", "bold","plain")) + 
  geom_text(aes(x = 1.5, label = Wald),
        hjust = 0,
        fontface = ifelse(dep_df$Wald == "Wald", "bold","plain")) +
  geom_text(aes(x = 1.9, label = label),
        hjust = 0,
        fontface = ifelse(dep_df$label == "OR [95% CI]", "bold","plain")) +
  theme_void() +     
  coord_cartesian(ylim = c(1,length(dep_df$Variable)), xlim = c(0, 4))

@@

Depression Plot
```{r}
DEP_FP <- 
  dep_df |>
  ggplot(aes(y = reorder(Variable, -order))) +
  #take away background
  theme_classic() +
  #make the forrest plot
  geom_linerange(aes(xmin=OR_low, xmax=OR_high),size = 1, show.legend = FALSE,
                color = ifelse(dep_df$p.adjusted < 0.05, "blue", "darkgrey")) +
  geom_point(aes(x=OR), shape= 16,
             size=4,show.legend = FALSE,
             color = ifelse(dep_df$p.adjusted < 0.05, "blue", "darkgrey")) +
  geom_point(aes(x=OR), shape= 1,
             size=4,show.legend = FALSE, color = "white") +
    geom_point(aes(x=OR), shape= 1,
             size=4.1,show.legend = FALSE, color = "white")+
# geom_errorbar(aes(xmin=OR_low, xmax=OR_high),width =.6, show.legend = FALSE) +
  #change x axis name
  labs(
    x="Odds Ratio",
    # title = "    Odds of Meeting Physical Activity Guidelines",
    subtitle ="Odds of Depression Non-Response")+
  #adjust the dimentions. 
  coord_cartesian(ylim = c(1,  length(dep_df$Variable)),
                  xlim = c(0,2))+
  #add a line at 1 for reference 
  geom_vline(xintercept = 1,linetype="dashed",alpha = .50) + 
  #add anotations to help suggests what each side means.
  annotate("text", x = .6, y = length(dep_df$variable) -1 , label = "Less Likely", size= 4) +
  annotate("text", x = 1.4, y = length(dep_df$variable) -1, label = "More Likely",size= 4) +
  #Git rid of the Y - Axis
    theme(axis.line.y = element_blank(),
        axis.ticks.y= element_blank(),
        axis.text.y= element_blank(),
        axis.title.y= element_blank())

@@

```{r}
#Create order varaible in dataset to keep it the same as the regression

FP_anx <- read_csv("~/Downloads/FP.min.anx")
# FP_anx <- read_csv("~/Downloads/FP.1se.anx")

#Change the names of variables
# FP_anx$Variable = c("Age", "Unmarried", "Days Completed", 
#                     "Days Not Attended", "Anixety Disorder","Trauma Disorder", 
#                     "Other Disorder", "Co-Mood Disorder",  "Co-BPD", 
#                     "Co-SUD", "CUXOS Pre", "Post Coping", 
#                     "Post PMH", "Post Functioning", "Post Wellbeing")

FP_anx$order = c(seq(from=2, to=length(FP_anx$Variable) + 1,1))

FP_anx <- FP_anx |>
  mutate(
    sig = ifelse(p.adjusted <= 0.05, 16,1)
  )

FP_anx_m <- FP_anx |>
  ggplot(aes(y = reorder(Variable, -order), color = as.factor(sig))) +
  #take away background
  theme_classic() +
  #make the forrest plot
  geom_point(aes(x=OR), shape= FP_anx$sig,
               # ifelse(FP_anx$p.adjusted <= 0.05, 
               #                        16, # colored ones for significant varaibles
               #                        1), # uncolored ones for insignificant varaibles
             size=3.5,show.legend = FALSE) +
  geom_linerange(aes(xmin=OR_low, xmax=OR_high),size = .4, show.legend = FALSE) +
  geom_errorbar(aes(xmin=OR_low, xmax=OR_high),width =.5, show.legend = FALSE)+
  scale_color_manual(values = c("darkgrey","red"))+
  #change x axis name
  labs(
    x="Odds Ratio") +
    # title = "Odds of Anxiety Treatment Non-Response",
    # subtitle = "Based on Pre/Post CUXOS Scores in PHP program") +
  #adjust the dimentions. 
  coord_cartesian(ylim = c(1,length(FP_anx$Variable) + 1),
                  xlim = c(.25,2.5)) +
  #add a line at 1 for reference 
   geom_vline(xintercept = 1, linetype="dashed", alpha = .5) +
  #add anotations to help suggests what each side means.
  annotate("text", x = .6, y = length(FP_anx$Variable) + 1, label = "Less Likely", size= 3) +
  annotate("text", x = 1.5, y = length(FP_anx$Variable) + 1, label = "More Likely",size= 3) +
  #Git rid of the Y - Axis
    theme(axis.line.y = element_blank(),
        axis.ticks.y= element_blank(),
        axis.text.y= element_blank(),
        axis.title.y= element_blank())

FP_anx_m

FP_anx <- FP_anx |>
  # round estimates and 95% CIs to 2 decimal places for journal specifications
  mutate(across(
    c(OR, OR_low, OR_high),
    ~ str_pad(
      round(.x, 2),
      width = 4,
      pad = "0",
      side = "right"
    )
  ),
  # add an "-" between HR estimate confidence intervals
  estimate_lab = paste0(OR, " [", OR_low, "-", OR_high, "]")) |>
  # round p-values to two decimal places, except in cases where p < .001
  mutate(p.adjusted_fig = case_when(
    p.adjusted < .001 ~ "<0.001",
    round(p.adjusted, 2) == .05 ~ as.character(round(p.adjusted,3)),
    p.adjusted < .01 ~ str_pad( # if less than .01, go one more decimal place
      as.character(round(p.adjusted, 3)),
      width = 4,
      pad = "0",
      side = "right"
    ),
    TRUE ~ str_pad( # otherwise just round to 2 decimal places and pad string so that .2 reads as 0.20
      as.character(round(p.adjusted, 2)),
      width = 4,
      pad = "0",
      side = "right"
    )
  )) |>
  # add a row of data that are actually column names which will be shown on the plot in the next step
  bind_rows(
    data.frame(
      Variable = "Variable",
      estimate_lab = "Odds Ratio (95% CI)",
      OR_low = "",
      OR_high = "",
      p.adjusted_fig = "p value"
    )
  )

FP_anx[length(FP_anx$Variable),8] = 1
FP_anx

#arange the labels on top
      FP_anx<-mutate(FP_anx, top_row = 0)
      FP_anx[length(FP_anx$Variable),12] = 1
      FP_anx <- arrange(FP_anx,order)
FP_anx
    # plot the left side of the plot 
      FP_anx_L <- FP_anx %>% 
        ggplot(aes(y = reorder(Variable, -order))) +
        geom_text(aes(x = 0, label = Variable), hjust = 0, fontface = "bold")+
        geom_text(aes(x = 1, label = estimate_lab),
        hjust = 0,
        fontface = ifelse(FP_anx$estimate_lab == "Odds Ratio (95% CI)", "bold","plain")) +
        theme_void() +
        coord_cartesian(ylim = c(1,length(FP_anx$Variable)), xlim = c(0, 4))

FP_anx_L

FP_anx_R <-  
      FP_anx |>
      ggplot() +
        geom_text(aes(x = 0, y = reorder(Variable, -order), label = p.adjusted_fig), hjust = 0,
        fontface = ifelse(FP_anx$p.adjusted_fig == "p value", "bold", "plain")) +
        theme_void() +
        coord_cartesian(ylim = c(1,length(FP_anx$Variable)))

FP_anx

layout <- c(
  patchwork::area(t = 0, l = 0, b = 30, r = 35),
  patchwork::area(t = 0, l = 19, b = 30, r = 34),
  patchwork::area(t = 0, l = 30, b = 30, r = 40) 
  )

FP_anx_L + FP_anx_m + FP_anx_R + plot_layout(design = layout)

@@

## Depression Plot
```{r}
#Create order varaible in dataset to keep it the same as the regression

FP_dep <- read_csv("~/Downloads/FP.min.dep")

#rename the variables for the figure

# FP_dep$Variable = c(
#                      "Days Not Attended",
#                     "Post Coping", 
#                     "Post PMH", "Post Functioning", "Post Wellbeing")

FP_dep$order = c(seq(from=2, to=length(FP_dep$Variable) + 1,1))

FP_dep <- FP_dep |>
  mutate(
    sig = ifelse(p.adjusted <= 0.05, 16,1)
  )

>>>>

## Read in the dataset. 
```{r}

#set path for working directory for PC or MAC
wd_path <- 
  ifelse(Sys.info()[[1]] == "Windows","C:/Users/troyh/OneDrive - University of Kentucky/Coding/R working directory/",
         ifelse(Sys.info()[[1]] == "Darwin", "~/Desktop/Coding/R working directory/","¿¿Donde Estoy??"
         ))

#Set path for directory with data files for PC or MAC
data_path <- 
  ifelse(Sys.info()[[1]] == "Windows","C:/Users/troyh/OneDrive - University of Kentucky/Coding/data/",
         ifelse(Sys.info()[[1]] == "Darwin", "~/Desktop/Coding/Data/","¿¿Donde Estoy??"
         ))

#read main File
Mothership <- read_sav(paste0(data_path,"PHPoutcome_clean.sav"))
#DF_1<- read_sav("~/Desktop/Coding/data/PHPoutcome_clean.sav")
```

@@

####  Export as CSV
write.csv(Mothership,paste0(data_path,"Mothership_paper"))

@@

### Export as CSV
write.csv(Mothership,paste0(data_path,"Mothership_Diag_treat.csv"))

@@

install.packages('naniar')
library(naniar)
vis_miss(Mothership_Missing)
```

@@

#2. JT classification for anxiety
JTRCI (data = RCI_df_anx2, 
                  pre = "pre", 
                  post = "post", 
                  ppid = "ID1", 
                  reliability = .74, 
                  indextype = "JT", 
                  plottitle = "JT Indices For Anxiety")

ANX_JT_smol<- JTRCIdf
view(DEP_JT_smol)

@@

write_csv(table1_tab_anx,paste0("C:/Users/troyh/OneDrive - University of Kentucky/Coding/data/table1_tab_anx_test.csv"))

@@

table1_tab_dep
write_csv(table1_tab_dep,paste0(data_path,"table1_tab_dep_test.csv"))

@@

ataset visualizatoin
```{r}
# install.packages("ggdist")
library("ggdist")

anx_fig <- Mothership_lasso_anx |>
  mutate(
      Anxiety_Responder = as.factor(recode(Anxiety_Responder,
        "Non-Responder" = paste0("Non-Responder (n=",summary(Mothership_lasso_anx$Anxiety_Responder)[[2]],")"),
        "Responder" = paste0("Responder (n=",summary(Mothership_lasso_anx$Anxiety_Responder)[[1]],")")
      )))

dep_fig <- Mothership_lasso_dep |>
  mutate(
      Depression_Responder = as.factor(recode(Depression_Responder,
        "Non-Responder" = paste0("Non-Responder (n=",summary(Mothership_lasso_dep$Depression_Responder)[[2]],")"),
        "Responder" = paste0("Responder (n=",summary(Mothership_lasso_dep$Depression_Responder)[[1]],")")
      )))

subset(dep_fig, !is.na(Depression_Responder)) |>
  ggplot(aes(x=CUDOS_pre, y=CUDOS_post, color=Depression_Responder)) +
  geom_point(position = position_jitter(.3),size=2,alpha=.75)+
  # geom_jitter(size=2,alpha=.75)+
  theme_classic()+
  scale_color_manual(values=c("darkgrey","#23c4cc"))+
  geom_abline(intercept = 0, slope = 1,linetype='dotted',size=.75)+
  geom_abline(intercept = 13, slope = 1, col = 'black',size=1)+
  geom_abline(intercept = -13, slope = 1, col = 'black',size=1)+
  geom_hline(yintercept =21, linetype = 'dashed',size = 1) +
    labs(
    title="         RCI Analysis of Depression Treatment Response\n",
    color = "  Depression Response",
    x = "Pre CUDOS",
    y= " Post CUDOS"
  )

subset(anx_fig, !is.na(Anxiety_Responder)) |>
  ggplot(aes(x=CUXOS_pre, y=CUXOS_post, color=Anxiety_Responder)) +
  geom_point(position = position_jitter(.3),size=2,alpha=.75)+
  # geom_jitter(size=2,alpha=.75)+
  theme_classic()+
  scale_color_manual(values=c("darkgrey","#e6402e"))+
  geom_abline(intercept = 0, slope = 1,linetype='dotted',size=.75)+
  geom_abline(intercept = 21, slope = 1, col = 'black',size=1)+
  geom_abline(intercept = -21, slope = 1, col = 'black',size=1)+
  geom_hline(yintercept =16.6, linetype = 'dashed',size = 1)+
  labs(
    title="           RCI Analysis of Anxiety Treatment Response\n",
    color = " Anxiety Response",
    x = "Pre CUXOS",
    y= " Post CUXOS"
  )

```{r}
# 
# Mothership_lasso|>
# ggplot( mapping=aes(x=Trauma_C)) +
#   geom_bar()
# 
# Mothership_lasso|>
# ggplot( mapping=aes(x= Current_Dx)) +
#         geom_histogram() +
#     theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
#   theme(panel.background=NULL)+
#   theme(legend.title = element_blank()) 
#

@@

```{r}
# 
# 
# FP_dep_m <- FP_dep |>
#   ggplot(aes(y = reorder(Variable, -order), color =as.factor(sig))) +
#   #take away background
#   theme_classic() +
#   #make the forrest plot
#   geom_point(aes(x=OR), shape= FP_dep$sig,
#                # ifelse(FP_dep$p.adjusted <= 0.05, 
#                #                        16, # colored ones for significant varaibles
#                #                        1), # uncolored ones for insignificant varaibles
#              size=4,show.legend = FALSE) +
#   geom_linerange(aes(xmin=OR_low, xmax=OR_high),size = .4, show.legend = FALSE) +
#   geom_errorbar(aes(xmin=OR_low, xmax=OR_high),width =.35, show.legend = FALSE)+
#   scale_color_manual(values = c("darkgrey","blue"))+
#   #change x axis name
#   labs(
#     x="Odds Ratio") +
#     # title = "Odds of Anxiety Treatment Non-Response",
#     # subtitle = "Based on Pre/Post CUXOS Scores in PHP program") +
#   #adjust the dimentions. 
#   coord_cartesian(ylim = c(1,length(FP_dep$Variable) + 1),
#                   xlim = c(.25,3.0)) +
#   #add a line at 1 for reference 
#    geom_vline(xintercept = 1, linetype="dashed", alpha = .5) +
#   #add anotations to help suggests what each side means.
#   annotate("text", x = .5, y = length(FP_dep$Variable) + 1, label = "Less Likely", size= 4) +
#   annotate("text", x = 1.5, y = length(FP_dep$Variable) + 1, label = "More Likely",size= 4) +
#   #Git rid of the Y - Axis
#     theme(axis.line.y = element_blank(),
#         axis.ticks.y= element_blank(),
#         axis.text.y= element_blank(),
#         axis.title.y= element_blank())
#

@@

#####  using 1se
# Final model with lambda.1se
lasso.model.1se.dep <- glmnet(x.dep, y.dep, alpha = 1, family = "binomial",
                      lambda = cv.lasso.dep$lambda.1se,standardized = TRUE)
# Make prediction on test data
x.test <- model.matrix(Depression_Responder ~., test.data)[,-1]
probabilities.1se <- lasso.model.1se.dep %>% predict(newx = x.test,type ="response")
predicted.classes.1se <- ifelse(probabilities.1se > 0.5, "Responder", "Non-Responder")

# Model accuracy rate
observed.classes <- test.data$Depression_Responder
Mean.predict.1se.dep <- mean(predicted.classes.1se == observed.classes)

@@

# Make predictions
probabilities.full <- full.model.dep %>% predict(test.data, type = "response")
predicted.classes.full <- ifelse(probabilities.full > 0.5, "Responder", "Non-Responder")
# Model accuracy
observed.classes.full <- test.data$Depression_Responder
Mean.predict.full.model.dep <- mean(predicted.classes.full == observed.classes)

@@

tmp_coeffs <- coef(lasso.model.min.dep, s = "lambda.min")
Dep_coefs <-tmp_coeffs@Dimnames[[1]][tmp_coeffs@i + 1]
Dep_reg_coefs <- Dep_coefs[2:length(Dep_coefs)]
Dep_reg_coefs
```

@@

write_csv(FP.min.dep, paste0(data_path,"FP.min.dep"))
```
1se -
```{r}
tmp_coeffs <- coef(lasso.model.1se.dep, s = "lambda.1se")
Dep_coefs <-tmp_coeffs@Dimnames[[1]][tmp_coeffs@i + 1]
Dep_reg_coefs <- Dep_coefs[2:length(Dep_coefs)]
Dep_reg_coefs

@@

write_csv(FP.1se.dep, paste0(data_path,"FP.1se.dep"))
```

@@

write_csv(FP.min.dep, paste0(data_path,"FP.min.dep"))

@@

write_csv(dep_df, paste0(data_path,"dep_df"))
```

@@

write_csv(FP.min.anx, paste0(data_path,"FP.min.anx"))

@@

# write_csv(anx_df, "~/Downloads/anx_df")

@@

Anxiety Plot
```{r}
ANX_FP <- 
  anx_df |>
  ggplot(aes(y = reorder(Variable, -order))) +
  #take away background
  theme_classic() +
  #make the forrest plot
  geom_linerange(aes(xmin=OR_low, xmax=OR_high),size = 1, show.legend = FALSE,
                color = ifelse(anx_df$p.adjusted < 0.05, "#e6402e", "darkgrey")) +
  geom_errorbar(aes(xmin=OR_low, xmax=OR_high),width =.3, show.legend = FALSE,
                color = ifelse(anx_df$p.adjusted < 0.05, "#e6402e", "darkgrey"))+
      geom_point(aes(x=OR), shape= 16,
             size=5,show.legend = FALSE, color = "white")+
    geom_point(aes(x=OR), shape= 16,
             size=4,show.legend = FALSE,
             color = ifelse(anx_df$p.adjusted < 0.05, "#e6402e", "darkgrey")) +
# geom_errorbar(aes(xmin=OR_low, xmax=OR_high),width =.6, show.legend = FALSE) +
  #change x axis name
  labs(
    x="Odds Ratio",
    # title = "    Odds of Meeting Physical Activity Guidelines",
    subtitle ="Odds of Anxiety Non-Response")+
  #adjust the dimentions. 
  coord_cartesian(ylim = c(1,  length(anx_df$Variable)))+
  #add a line at 1 for reference 
  geom_vline(xintercept = 1,linetype="dashed",alpha = .50) + 
  #add anotations to help suggests what each side means.
  annotate("text", x = .6, y = length(anx_df$Variable) -1 , label = "Less Likely", size= 4) +
  annotate("text", x = 1.4, y = length(anx_df$Variable) -1, label = "More Likely",size= 4) +
  #Git rid of the Y - Axis
    theme(axis.line.y = element_blank(),
        axis.ticks.y= element_blank(),
        axis.text.y= element_blank(),
        axis.title.y= element_blank())
```

```{r}
ANX_text <- 
  anx_df |>
  ggplot(aes(y = reorder(Variable, -order))) +
  geom_text(aes(x = 0, label = Variable), hjust = 0,
        fontface = ifelse(anx_df$Variable == "Variable","bold","plain")) +
  geom_text(aes(x = 1.1, label = Beta),
        hjust = 0,
        fontface = ifelse(anx_df$Beta == "Beta", "bold","plain")) + 
  geom_text(aes(x = 1.5, label = Wald),
        hjust = 0,
        fontface = ifelse(anx_df$Wald == "Wald", "bold","plain")) +
  geom_text(aes(x = 1.9, label = label),
        hjust = 0,
        fontface = ifelse(anx_df$label == "OR [95% CI]", "bold","plain")) +
  theme_void() +     
  coord_cartesian(ylim = c(1,length(anx_df$Variable)), xlim = c(0, 4))

@@

Depression Plot
```{r}
DEP_FP <- 
  dep_df |>
  ggplot(aes(y = reorder(Variable, -order))) +
  #take away background
  theme_classic() +
  #make the forrest plot
    geom_linerange(aes(xmin=OR_low, xmax=OR_high),size = 1, show.legend = FALSE,
                color = ifelse(dep_df$p.adjusted < 0.05, "#23c4cc", "darkgrey")) +
    geom_errorbar(aes(xmin=OR_low, xmax=OR_high),width =.4, show.legend = FALSE,
                color = ifelse(dep_df$p.adjusted < 0.05, "#23c4cc", "darkgrey")) +
  # geom_errorbar(aes(xmin=OR_low, xmax=OR_high),width =.35, show.legend = FALSE,
                # color = ifelse(dep_df$p.adjusted < 0.05, "#23c4cc", "darkgrey"))+
      geom_point(aes(x=OR), shape= 16,
             size=5,show.legend = FALSE, color = "white")+
    geom_point(aes(x=OR), shape= 16,
             size=4,show.legend = FALSE,
             color = ifelse(dep_df$p.adjusted < 0.05, "#23c4cc", "darkgrey")) +

  #change x axis name
  labs(
    x="Odds Ratio",
    # title = "    Odds of Meeting Physical Activity Guidelines",
    subtitle ="Odds of Depression Non-Response") +
  #adjust the dimentions. 
  coord_cartesian(ylim = c(1,  length(dep_df$Variable)),
                  xlim = c(0.4,2)) +
  #add a line at 1 for reference 
  geom_vline(xintercept = 1,linetype="dashed",alpha = .50) +
  #add anotations to help suggests what each side means.
  annotate("text", x = .6, y = length(dep_df$Variable) -1 , label = "Less Likely", size= 4) +
  annotate("text", x = 1.4, y = length(dep_df$Variable) -1, label = "More Likely",size= 4) +
  #Git rid of the Y - Axis
    theme(axis.line.y = element_blank(),
        axis.ticks.y= element_blank(),
        axis.text.y= element_blank(),
        axis.title.y= element_blank())

@@

# #Create order varaible in dataset to keep it the same as the regression
# 
# FP_anx <- read_csv("~/Downloads/FP.min.anx")
# # FP_anx <- read_csv("~/Downloads/FP.1se.anx")
# 
# #Change the names of variables
# # FP_anx$Variable = c("Age", "Unmarried", "Days Completed", 
# #                     "Days Not Attended", "Anixety Disorder","Trauma Disorder", 
# #                     "Other Disorder", "Co-Mood Disorder",  "Co-BPD", 
# #                     "Co-SUD", "CUXOS Pre", "Post Coping", 
# #                     "Post PMH", "Post Functioning", "Post Wellbeing")
# 
# FP_anx$order = c(seq(from=2, to=length(FP_anx$Variable) + 1,1))
# 
# FP_anx <- FP_anx |>
#   mutate(
#     sig = ifelse(p.adjusted <= 0.05, 16,1)
#   )
# 
# FP_anx_m <- FP_anx |>
#   ggplot(aes(y = reorder(Variable, -order), color = as.factor(sig))) +
#   #take away background
#   theme_classic() +
#   #make the forrest plot
#   geom_point(aes(x=OR), shape= FP_anx$sig,
#                # ifelse(FP_anx$p.adjusted <= 0.05, 
#                #                        16, # colored ones for significant varaibles
#                #                        1), # uncolored ones for insignificant varaibles
#              size=3.5,show.legend = FALSE) +
#   geom_linerange(aes(xmin=OR_low, xmax=OR_high),size = .4, show.legend = FALSE) +
#   geom_errorbar(aes(xmin=OR_low, xmax=OR_high),width =.5, show.legend = FALSE)+
#   scale_color_manual(values = c("darkgrey","red"))+
#   #change x axis name
#   labs(
#     x="Odds Ratio") +
#     # title = "Odds of Anxiety Treatment Non-Response",
#     # subtitle = "Based on Pre/Post CUXOS Scores in PHP program") +
#   #adjust the dimentions. 
#   coord_cartesian(ylim = c(1,length(FP_anx$Variable) + 1),
#                   xlim = c(.25,2.5)) +
#   #add a line at 1 for reference 
#    geom_vline(xintercept = 1, linetype="dashed", alpha = .5) +
#   #add anotations to help suggests what each side means.
#   annotate("text", x = .6, y = length(FP_anx$Variable) + 1, label = "Less Likely", size= 3) +
#   annotate("text", x = 1.5, y = length(FP_anx$Variable) + 1, label = "More Likely",size= 3) +
#   #Git rid of the Y - Axis
#     theme(axis.line.y = element_blank(),
#         axis.ticks.y= element_blank(),
#         axis.text.y= element_blank(),
#         axis.title.y= element_blank())
# 
# FP_anx_m
# 
# FP_anx <- FP_anx |>
#   # round estimates and 95% CIs to 2 decimal places for journal specifications
#   mutate(across(
#     c(OR, OR_low, OR_high),
#     ~ str_pad(
#       round(.x, 2),
#       width = 4,
#       pad = "0",
#       side = "right"
#     )
#   ),
#   # add an "-" between HR estimate confidence intervals
#   estimate_lab = paste0(OR, " [", OR_low, "-", OR_high, "]")) |>
#   # round p-values to two decimal places, except in cases where p < .001
#   mutate(p.adjusted_fig = case_when(
#     p.adjusted < .001 ~ "<0.001",
#     round(p.adjusted, 2) == .05 ~ as.character(round(p.adjusted,3)),
#     p.adjusted < .01 ~ str_pad( # if less than .01, go one more decimal place
#       as.character(round(p.adjusted, 3)),
#       width = 4,
#       pad = "0",
#       side = "right"
#     ),
#     TRUE ~ str_pad( # otherwise just round to 2 decimal places and pad string so that .2 reads as 0.20
#       as.character(round(p.adjusted, 2)),
#       width = 4,
#       pad = "0",
#       side = "right"
#     )
#   )) |>
#   # add a row of data that are actually column names which will be shown on the plot in the next step
#   bind_rows(
#     data.frame(
#       Variable = "Variable",
#       estimate_lab = "Odds Ratio (95% CI)",
#       OR_low = "",
#       OR_high = "",
#       p.adjusted_fig = "p value"
#     )
#   ) 
# 
# FP_anx[length(FP_anx$Variable),8] = 1
# FP_anx
# 
# #arange the labels on top
#       FP_anx<-mutate(FP_anx, top_row = 0)
#       FP_anx[length(FP_anx$Variable),12] = 1
#       FP_anx <- arrange(FP_anx,order)
# FP_anx
#     # plot the left side of the plot 
#       FP_anx_L <- FP_anx %>% 
#         ggplot(aes(y = reorder(Variable, -order))) +
#         geom_text(aes(x = 0, label = Variable), hjust = 0, fontface = "bold")+
#         geom_text(aes(x = 1, label = estimate_lab),
#         hjust = 0,
#         fontface = ifelse(FP_anx$estimate_lab == "Odds Ratio (95% CI)", "bold","plain")) +
#         theme_void() +
#         coord_cartesian(ylim = c(1,length(FP_anx$Variable)), xlim = c(0, 4))
# 
# FP_anx_L
# 
# FP_anx_R <-  
#       FP_anx |>
#       ggplot() +
#         geom_text(aes(x = 0, y = reorder(Variable, -order), label = p.adjusted_fig), hjust = 0,
#         fontface = ifelse(FP_anx$p.adjusted_fig == "p value", "bold", "plain")) +
#         theme_void() +
#         coord_cartesian(ylim = c(1,length(FP_anx$Variable)))
#         
# FP_anx
# 
# library("patchwork")
# 
# layout <- c(
#   patchwork::area(t = 0, l = 0, b = 30, r = 35),
#   patchwork::area(t = 0, l = 19, b = 30, r = 34),
#   patchwork::area(t = 0, l = 30, b = 30, r = 40) 
#   )
# 
# FP_anx_L + FP_anx_m + FP_anx_R + plot_layout(design = layout)

@@

## Depression Plot
# #Create order varaible in dataset to keep it the same as the regression
# 
# 
# 
# FP_dep <- read_csv("~/Downloads/FP.min.dep")
# 
# #rename the variables for the figure
# 
# # FP_dep$Variable = c(
# #                      "Days Not Attended",
# #                     "Post Coping", 
# #                     "Post PMH", "Post Functioning", "Post Wellbeing")
# 
# 
# FP_dep$order = c(seq(from=2, to=length(FP_dep$Variable) + 1,1))
# 
# FP_dep <- FP_dep |>
#   mutate(
#     sig = ifelse(p.adjusted <= 0.05, 16,1)
#   )
# 
# FP_dep_m <- FP_dep |>
#   ggplot(aes(y = reorder(Variable, -order), color =as.factor(sig))) +
#   #take away background
#   theme_classic() +
#   #make the forrest plot
#   geom_point(aes(x=OR), shape= FP_dep$sig,
#                # ifelse(FP_dep$p.adjusted <= 0.05, 
#                #                        16, # colored ones for significant varaibles
#                #                        1), # uncolored ones for insignificant varaibles
#              size=4,show.legend = FALSE) +
#   geom_linerange(aes(xmin=OR_low, xmax=OR_high),size = .4, show.legend = FALSE) +
#   geom_errorbar(aes(xmin=OR_low, xmax=OR_high),width =.35, show.legend = FALSE)+
#   scale_color_manual(values = c("darkgrey","blue"))+
#   #change x axis name
#   labs(
#     x="Odds Ratio") +
#     # title = "Odds of Anxiety Treatment Non-Response",
#     # subtitle = "Based on Pre/Post CUXOS Scores in PHP program") +
#   #adjust the dimentions. 
#   coord_cartesian(ylim = c(1,length(FP_dep$Variable) + 1),
#                   xlim = c(.25,3.0)) +
#   #add a line at 1 for reference 
#    geom_vline(xintercept = 1, linetype="dashed", alpha = .5) +
#   #add anotations to help suggests what each side means.
#   annotate("text", x = .5, y = length(FP_dep$Variable) + 1, label = "Less Likely", size= 4) +
